Papers

### 2024-02-09 papers.qmd
update for 2024
fix link

A. McCombs, M. A. Ausdemore, K. Goode, J. G. Huerta, K. Shuler, **J. D. Tucker**, A. Zhang, and D. Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*. submitted, 2023.

@@

## Invited Talks
"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/ASA_23_Calibration/index.html)

>>>>

## 2024
A. McCombs, M. A. Ausdemore, K. Goode, J. G. Huerta, K. Shuler, **J. D. Tucker**, A. Zhang, and D. Ries, “Inverse prediction of PuO2 processing conditions using Bayesian seemingly unrelated regression with functional data”, *Frontiers in Nuclear Engineering-Nuclear Materials*. submitted, 2023.

@@

## Invited Talks
"Elasic Bayesian Model Calibration" *ASA SDNS Webinar*, December 04, 2023, [Slides](https://jdtuck.github.io/presentations/ASA_23_Calibration/index.html)
